\problemname{The Wizard Theodor}

A small army of $N$ monsters is just outside Tästerås! Now it is up to the wizard Theodor to defeat
them and save the city. Each monster has a certain amount of life points. To damage the monsters,
Theodor can fire magical explosions. Each time he fires an explosion, he targets a specific monster.
Then, the following occurs:

\begin{itemize}
  \item All monsters lose $A$ life points due to the explosion.
  \item The monster that Theodor targeted loses an additional $S$ life points, as it is at the center of
  the explosion. Thus, the targeted monster loses a total of $S + A$ life points from that explosion.
\end{itemize}

He can freely choose which monster to target each time he fires an explosion. Since firing explosions
is exhausting, he wants to know the minimum number of explosions he needs to fire to defeat all the
monsters if he targets them optimally.

\section*{Input}  
The first line of input contains three integers, $N$ ($1 \leq N \leq 10$), $S$ ($1 \leq S \leq 10^9$), and $A$ ($0 \leq A \leq 10^9$), 
which are the three values described above.  

The second line contains $N$ integers $h_1, h_2, \ldots, h_N$ ($1 \leq h_i \leq 10^9$), representing the
life points of each monster.  

\section*{Output}  
Print the minimum number of explosions Theodor needs to fire to defeat all the monsters.  

\section*{Scoring}
Your solution will be tested on a set of test groups, each worth a number of points. Each test group contains
a set of test cases. To get the points for a test group you need to solve all test cases in the test group.

\noindent
\begin{tabular}{| l | l | p{12cm} |}
  \hline
  \textbf{Group} & \textbf{Points} & \textbf{Constraints} \\ \hline
  $1$    & $20$       & $A = 0$ \\ \hline
  $2$    & $35$       & $h_i \leq 100$ \\ \hline
  $3$    & $5$        & $A \leq 10^5$ \\ \hline
  $4$    & $40$       & No additional constraints. \\ \hline
\end{tabular}

\section*{Explanation of Sample 1}
An optimal way to fire explosions is as follows:  
\begin{enumerate}  
  \item Fire an explosion at the monster with 7 life points. The monsters now have \verb+4,1,2+ life points remaining.  
  \item Fire an explosion at the monster with 4 life points remaining. The monster with 1 life point is defeated. The remaining monsters now have \verb+1,1+ life points.  
  \item Fire an explosion at any of the remaining monsters. Now all the monsters have been defeated, and Theodor is done.  
\end{enumerate}
