\problemname{Programmeringsolympiaden's Budget}

Programmeringsolympiaden (PO) must write a budget every year, which then needs to be approved by the
treasurer Emil. This year, the PO leadership has proposed some rather wild ideas, such as buying
2000 ducks and purchasing a PO-yacht to sail to the IOI (the world finals of competitive programming).
Emil finds it difficult to determine whether the budget is reasonable or not.

A budget consists of several revenues and expenses.
To assess whether the budget is reasonable, Emil wants to calculate whether the proposed budget would
result in Programmeringsolympiaden making a profit, a loss, or breaking even financially. Can you write a program to help Emil decide this?

\section*{Input}
The first line of input contains the integer $N$ ($1 \leq N \leq 30$), the number of revenues/expenses in the budget.

This is followed by all $N$ revenues/expenses. Each is described over two lines: first, a description of what it is,
a string of at most 30 characters. For simplicity, the string contains no spaces.  
The next line contains an integer $K$ ($-10^7 \leq K \leq 10^7$). If $K$ is positive, it represents a revenue of $K$ kronor;
otherwise, it is an expense of $-K$ kronor.

\section*{Output}
\begin{itemize}
  \item If the budget would lead to PO making money, print ``Usch, vinst''. This translates to ``Ew, profit''.
  \item If the budget breaks even, print ``Lagom''. This translates to ``Just right''.
  \item If the budget would lead to a loss, print ``Nekad''. This translates to ``Denied''.
\end{itemize}
Note that you should not print the quotation marks.

\section*{Scoring}
Your solution will be tested on a set of test groups, each worth a number of points. Each test group contains
a set of test cases. To get the points for a test group you need to solve all test cases in the test group.

\noindent
\begin{tabular}{| l | l | p{12cm} |}
  \hline
  \textbf{Group} & \textbf{Points} & \textbf{Constraints} \\ \hline
  $1$    & $20$       & $K = 0$ for all $K$. \\ \hline 
  $2$    & $30$       & $K \geq 0$ for all $K$. \\ \hline
  $3$    & $50$       & No additional constraints. \\ \hline
\end{tabular}

\section*{Explanation of Sample 1}  
Since the yacht costs much more than what PO receives from the sponsorship, the budget results in a loss, and thus the correct answer is \texttt{Nekad}.  

\section*{Explanation of Sample 2}  
Even though there are some expenses, their total is less than the revenue from the sponsorship.  

\section*{Explanation of Sample 3}  
If there is no PO at all, there are neither revenues nor expenses, which results in breaking even.  

\section*{Explanation of Sample 4}  
Here, the revenues exactly match the expenses, which also results in breaking even. 
