\problemname{Truls' Troubles}

Truls and Henry are playing table tennis against each other.

Both Truls and Henry strongly dislike math.  
More than anything, they hate calculating how many points each of them has during the game.  
To simplify scoring, they have come up with their own solution:

Instead of constantly keeping track of their points, they write a ``\texttt{T}'' if Truls
scores a point and an ``\texttt{H}'' if Henry scores a point, immediately after each won rally.

When Truls and Henry play table tennis, the scoring system works according to these three rules:  
\begin{enumerate}
  \item One point is awarded after each rally.  
  \item A player wins a match if both of the following conditions are met:  
  \begin{itemize}
    \item The player leads by at least 2 points over their opponent.  
    \item The player has at least 11 points.  
  \end{itemize}  
  For example, if Truls has 11 points and Henry has 9 points, Truls is declared the winner.
  But if Truls has 11 points and Henry has 10 points, there is no winner yet.  

  \item When a player wins according to the criteria above, the points for both players are reset to zero, and a new match begins.  
\end{enumerate}  

Now Truls and Henry have been playing for a long time, and both want to know the current score.  
They ask you to write a program that calculates the current score for them based on their notes.

\section*{Input}
Input consists of Truls and Henry's notes, which consists of multiple letters on a single line. The number of letters is between 1 and 30.  
Each letter will be either ``\texttt{T}'' or ``\texttt{H}''.

\section*{Output}
Print the score of the ongoing match as $T$-$H$, where $T$ is
the number of points Truls has, and $H$ is the number of points Henry has.

\section*{Scoring}
Your solution will be tested on a set of test groups, each worth a number of points. Each test group contains
a set of test cases. To get the points for a test group you need to solve all test cases in the test group.

\noindent
\begin{tabular}{| l | l | p{12cm} |}
  \hline
  \textbf{Group} & \textbf{Points} & \textbf{Constraints} \\ \hline
  $1$    & $40$       & A match always ends as soon as one player reaches 11 points. \\ \hline
  $2$    & $60$       & No additional constraints. \\ \hline
\end{tabular}

\section*{Explanation of Sample 1}
In total, Truls has won 4 points, and Henry has won 5 points.

\section*{Explanation of Sample 2}
Since Truls won the match when the score reached \texttt{11-0}, the score was reset to \texttt{0-0}.

\section*{Explanation of Sample 3}
Even though both have more than 11 points, neither leads by 2 points. Therefore, no winner has been declared yet.

\section*{Explanation of Sample 4}
This game is a continuation of sample 3, where Henry wins the match after scoring two more points.  
The score is reset, and Henry then wins another point. Therefore, the score is \texttt{0-1}.

